Figures

### 2020-04-03 figures/01_geometry.Rmd
add one to one line and better legend placement

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) + 
  geom_point() +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")

gg_scatter_reservoir <- ggplot(data = dplyr::filter(
  st_drop_geometry(dt), !is.na(reservoir_class))) + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = reservoir_class)) +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")
```

@@

gg_slope_shape <- ggplot(data = test, 
                         aes(slope_mean, inlake_slope.y, 
                             color = shape_class)) + 
    geom_point() +
  geom_smooth(data = dplyr::filter(test, shape_class != "neither"), 
              method = "lm", se = FALSE) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "")

gg_slope_reservoir <- ggplot(data = dplyr::filter(test, !is.na(reservoir_class)), 
                             aes(slope_mean, inlake_slope.y, 
                                 color = reservoir_class)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "")
```

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5, fig.height=4.2}
theme_opts <- theme(legend.position = "none")

legend_shape     <- cowplot::get_legend(gg_scatter_shape)
legend_reservoir <- cowplot::get_legend(gg_scatter_reservoir + labs(color = ""))
legend_panel     <- cowplot::plot_grid(legend_shape, legend_reservoir, 
                                       ncol = 1, 
                                       align = "hv")

cowplot::plot_grid(
  cowplot::plot_grid(gg_scatter_shape + 
                       labs(color = "") +
                       # theme(axis.title.x = element_blank()) +
                       theme_opts,
                     gg_scatter_reservoir + 
                       labs(color = "") +
                       theme(#axis.title.x = element_blank(), 
                             axis.title.y = element_blank()) +
                       theme_opts,
                     gg_slope_shape +
                       theme_opts,
                     gg_slope_reservoir + 
                       theme(axis.title.y = element_blank()) +
                       theme_opts, 
                     rel_widths = c(1, 0.93, 1, 1)), 
  legend_panel, rel_widths = c(1, 0.2)
)
```

>>>>

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) + 
  geom_point(size = 1) +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")

gg_scatter_reservoir <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(reservoir_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  ggplot() + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = reservoir_class), 
             size = 1) +
  scale_color_discrete(labels = c("NL     ", "Res")) + 
  # geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")
```

@@

gg_slope_shape <- ggplot(data = test) + 
  geom_point(aes(slope_mean, inlake_slope.y, 
                             color = shape_class), size = 1) +
  geom_smooth(aes(slope_mean, inlake_slope.y, 
                             color = shape_class), data = dplyr::filter(test, shape_class != "neither"), 
              method = "lm", se = FALSE) +
  geom_segment(aes(x = 0, xend = 0.35, y = 0, yend = 0.35), 
               linetype = "dashed", size = 0.4) +
  # geom_abline(slope = 1, intercept = 0) +
  xlab("Nearshore slope (mean)") +
  ylab("Inlake slope") +
  labs(color = "")

gg_slope_reservoir <- ggplot(data = dplyr::filter(test, !is.na(reservoir_class))) +
  geom_point(aes(slope_mean, inlake_slope.y, 
                                 color = reservoir_class), size = 1) +
  geom_smooth(aes(slope_mean, inlake_slope.y, 
                                 color = reservoir_class), 
              method = "lm", se = FALSE) +
  geom_segment(aes(x = 0, xend = 0.35, y = 0, yend = 0.35), 
               linetype = "dashed", size = 0.4) +
  xlab("Nearshore slope (mean)") +
  ylab("Inlake slope") +
  labs(color = "")
```

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5.5, fig.height=4.2}
theme_opts <- cowplot::theme_cowplot() + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 11))
gg_spacer <- ggplot() + geom_blank() + theme(panel.background = element_blank())

legend_shape     <- cowplot::get_legend(gg_scatter_shape +
                                          theme(legend.direction = "horizontal"))
legend_reservoir <- cowplot::get_legend(gg_scatter_reservoir + labs(color = "") +
                                          theme(legend.direction = "horizontal"))
legend_panel     <- cowplot::plot_grid(gg_spacer, legend_shape, 
                                       gg_spacer, legend_reservoir, 
                                       nrow = 1, rel_widths = c(0.1, 1, 0.08, 1),
                                       align = "hv")

cowplot::plot_grid(
  cowplot::plot_grid(
  cowplot::plot_grid(gg_scatter_shape + 
                       labs(color = "") +
                       # theme(axis.title.x = element_blank()) +
                       theme_opts,
                     gg_scatter_reservoir + 
                       labs(color = "") +
                       theme(#axis.title.x = element_blank(), 
                             axis.title.y = element_blank()) +
                       theme_opts, 
                     ncol = 2),
  cowplot::plot_grid(ggplot() + geom_blank() + 
                       theme_opts + theme(axis.line = element_blank()), 
                     gg_slope_shape +
                       theme_opts,
                     gg_slope_reservoir + 
                       theme(axis.title.y = element_blank()) +
                       theme_opts,
                     ncol = 3, rel_widths = c(0.08, 1, 1)), 
                     rel_widths = c(1, 1), nrow = 2), 
 legend_panel, rel_heights = c(1, 0.12), ncol = 1
)
```

### 2020-04-03 manuscript/figures.Rmd
add one to one line and better legend placement

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) nearshore slope versus inlake slope.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```

>>>>

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) nearshore slope versus inlake slope. Also shown is a 1:1 line for comparison.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```
